Navigating to a greener Europe with 24/7 hourly clean electricity procurement

### 2023-10-02 manuscript/manuscript.tex
backmatter: generalise abbrev list
references: connect zotero export to project .bib

\hfuzz=5.002pt %https://tex.stackexchange.com/questions/13715/how-to-suppress-overfull-hbox-warnings-up-to-some-maximum

@@

% acronyms
\makeglossaries
\newacronym{tes}{TES}{Thermal Energy Storage (in form of water tanks)}
\newacronym{chp}{CHP}{Combined Heat and Power plant}
\newacronym{cop}{COP}{Coefficient of Performance}
\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
\newacronym{PV}{PV}{Solar photovoltaics}
\newacronym{ghg}{GHG}{Greenhouse gas}
\newacronym{EU}{EU}{European Union}
\newacronym{dea}{DEA}{Danish Energy Agency}
\newacronym{helmeth}{HELMETH}{Integrated High-Temperature Electrolysis and Methanation for Effective Power to Gas Conversion}
\newacronym{jrc}{JRC}{Joint Research Center}
\newacronym{ocgt}{OCGT}{Open Cycle Gas Turbine}
\newacronym{v2g}{V2G}{Vehicle to Grid}
\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}
\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{hvdc}{HVDC}{High Voltage Direct Current}
\newacronym{phs}{PHS}{Pumped Hydro Storage}
\newacronym{dac}{DAC}{Direct Air Capture}
\newacronym{sng}{SNG}{Synthetic Natural Gas}
\newacronym{fom}{FOM}{Fixed Operation and Maintenance costs}
\newacronym{vom}{VOM}{Variable Operation and Maintenance costs}
\newacronym{ppa}{PPA}{Power Purchase Agreement}
\newacronym{ptc}{PTC}{Production Tax Credit}
\newacronym{res}{RES}{Renewable Energy Sources}
\newacronym{necp}{NECP}{National Energy and Climate Plan}
\newacronym{ets}{ETS}{Emissions Trading System}
\newacronym{capex}{CAPEX}{Capital expenditures}
\newacronym{cfd}{CfD}{Contract for Difference}
\newacronym{cfe}{CFE}{Carbon-Free Electricity}
\newacronym{ci}{C\&I}{Corporate and Industry (sectors)}
\newacronym{ldes}{LDES}{Long Duration Energy Storage}

@@

This paper is an independent project, which is based on the third-party funded 
research work \cite{Riepin-report-2022}. This research work was supported by a grant from Google Inc.

@@

% tidy with https://flamingtempura.github.io/bibtex-tidy/
\addcontentsline{toc}{section}{References}
\renewcommand{\ttdefault}{\sfdefault}
\bibliography{references}

>>>>

\hfuzz=6.002pt %https://tex.stackexchange.com/questions/13715/how-to-suppress-overfull-hbox-warnings-up-to-some-maximum

@@

% acronyms
\makeglossaries

% Proper nouns
\newacronym{EU}{EU}{European Union}
\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
\newacronym{dea}{DEA}{Danish Energy Agency}
\newacronym{jrc}{JRC}{Joint Research Center}
\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}

% Enegy tech concepts
\newacronym{tes}{TES}{Thermal Energy Storage (in form of water tanks)}
\newacronym{chp}{CHP}{Combined Heat and Power plant}
\newacronym{cop}{COP}{Coefficient of Performance}
\newacronym{PV}{PV}{Solar photovoltaics}
\newacronym{ghg}{GHG}{Greenhouse gas}
\newacronym{helmeth}{HELMETH}{Integrated High-Temperature Electrolysis and Methanation for Effective Power to Gas Conversion}
\newacronym{ocgt}{OCGT}{Open Cycle Gas Turbine}
\newacronym{v2g}{V2G}{Vehicle to Grid}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{hvdc}{HVDC}{High Voltage Direct Current}
\newacronym{phs}{PHS}{Pumped Hydro Storage}
\newacronym{dac}{DAC}{Direct Air Capture}
\newacronym{sng}{SNG}{Synthetic Natural Gas}
\newacronym{res}{RES}{Renewable Energy Sources}
\newacronym{cfe}{CFE}{Carbon-Free Electricity}
\newacronym{ldes}{LDES}{Long Duration Energy Storage}
\newacronym{ccs}{CCS}{Carbon Capture and Sequestration}

% Energy economics and finance concepts
\newacronym{fom}{FOM}{Fixed Operation and Maintenance costs}
\newacronym{vom}{VOM}{Variable Operation and Maintenance costs}
\newacronym{capex}{CAPEX}{Capital expenditures}
\newacronym{opex}{OPEX}{Operational expenditures}
\newacronym{ppa}{PPA}{Power Purchase Agreement}
\newacronym{ptc}{PTC}{Production Tax Credit}
\newacronym{necp}{NECP}{National Energy and Climate Plan}
\newacronym{ets}{ETS}{Emissions Trading System}
\newacronym{cfd}{CfD}{Contract for Difference}

% Other
\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
\newacronym{ci}{C\&I}{Corporate and Industry (sectors)}

@@

This paper is an independent project, which is based on the third-party funded research work \cite{riepin-zenodo-systemlevel247}.
This research work was supported by a grant from Google Inc.

@@

% tidy with https://flamingtempura.github.io/bibtex-tidy/
\addcontentsline{toc}{section}{References}
\renewcommand{\ttdefault}{\sfdefault}
\bibliography{paper_247CFE}

### 2023-10-02 manuscript/sections/introduction.tex
finish results section
references: connect zotero export to project .bib

\textbf{Dummy abstract from ECEMP - to refine}

@@

For this reason, there is growing interest from corporations such as Google to match their demand with clean energy supply on a truly 24/7 basis. 
Achieving 24/7 Carbon-Free Energy (CFE) means that every kilowatt-hour of electricity consumption is met with carbon-free electricity sources, every hour of every day. 
Thus, this approach has the potential to eliminate all carbon emissions associated with Google's electricity use completely. 
In 2020 Google committed to the ambitious goal of operating entirely on a 24/7-CFE approach at all its data centres and campuses worldwide by 2030 \cite{Google-1}. 
Shortly after, Google published a policy roadmap on achieving the 24/7-CFE goal \cite{Google-2}.

>>>>

\textbf{Sketch introduction - to refine}

@@

For this reason, there is growing interest from corporations such as Google to match their demand with clean energy supply on a truly 24/7 basis. 
Achieving 24/7 Carbon-Free Energy (CFE) means that every kilowatt-hour of electricity consumption is met with carbon-free electricity sources, every hour of every day. 
Thus, this approach has the potential to eliminate all carbon emissions associated with Google's electricity use completely. 
In 2020 Google committed to the ambitious goal of operating entirely on a 24/7-CFE approach at all its data centres and campuses worldwide by 2030 \cite{google-247by2030}. 
Shortly after, Google published a policy roadmap on achieving the 24/7-CFE goal \cite{google-PolicyRoadmap}.

### 2023-10-02 manuscript/sections/methods.tex
manuscript results chapter
finish results section
references: connect zotero export to project .bib

\textbf{Dummy methods - to refine}

Methodologically, our modelling workflow is based on the PyPSA (Python for Power System Analysis)\footnote{PyPSA is available at \url{https://github.com/PyPSA/PyPSA}}—an open-source software toolbox for simulating and optimising modern energy systems at high resolution maintained by TU Berlin \cite{Brown-PyPSA,HORSCH-PyPSAEUR}. 
The model developed for this study optimises investment and operational decisions to meet projected electricity demand for the consumers performing clean energy procurement, as well as the demand for other consumers in the European electricity system, while meeting all relevant engineering, reliability, and policy constraints. 
This project is also developed as open-source.\footnote{247-CFE code is available at  \url{https://github.com/PyPSA/247-cfe}}

In this study, we implement a set of new constraints to model a situation when a fraction of corporate and industry (C\&I) demand commit to the 24/7-CFE goal. 
These constraints ensure that a portfolio of carbon-free generation located in the same market as the participating C\&I consumers covers their electricity demand profiles every hour of every day. 
The mathematical implementation allows for examining a scenario space when different shares of demand pursue the 24/7 approach with varying thresholds for meeting the hourly clean energy requirement (e.g. 90\%, 95\%, 100\%) using the definitions provided in Google's paper on methodologies and metrics \cite{Google-methods}.

@@

>>>>

\textbf{Sketch methods - to refine}

Methodologically, our modelling workflow is based on the PyPSA (Python for Power System Analysis)\footnote{PyPSA is available at \url{https://github.com/PyPSA/PyPSA}}—an open-source software toolbox for simulating and optimising modern energy systems at high resolution maintained by TU Berlin \cite{brownPyPSAPythonPower2018,horschPyPSAEurOpenOptimisation2018}. 
The model developed for this study optimises investment and operational decisions to meet projected electricity demand for the consumers performing clean energy procurement, as well as the demand for other consumers in the European electricity system, while meeting all relevant engineering, reliability, and policy constraints. 
This project is also developed as open-source.\footnote{247-CFE code is available at  \url{https://github.com/PyPSA/247-cfe}}

In this study, we implement a set of new constraints to model a situation when a fraction of corporate and industry (C\&I) demand commit to the 24/7-CFE goal. 
These constraints ensure that a portfolio of carbon-free generation located in the same market as the participating C\&I consumers covers their electricity demand profiles every hour of every day. 
The mathematical implementation allows for examining a scenario space when different shares of demand pursue the 24/7 approach with varying thresholds for meeting the hourly clean energy requirement (e.g. 90\%, 95\%, 100\%) using the definitions provided in Google's paper on methodologies and metrics \cite{google-methodologies}.

@@

\subsection{Scenario space}
\label{subsec:scenarios}

%TODO tech abbrev have to be defined here
% CCS and LDES

### 2023-10-02 manuscript/sections/results.tex
references: connect zotero export to project .bib

Voluntary procurement of clean electricity also helps decarbonise electricity system as a whole.
We explore this effect by plotting \co emissions in the local region of the participating consumers, i.e. Ireland.
Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2~Mt\co -- see a reference case in \cref{fig:10-2025-IE-p1-zone_emissions}.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021. A strong decreasing trend is expected, since Irish government has set ambitious targets to achieve a low-carbon energy system \cite{SEAI}.}
The modelling results show that if only 10\% of \gls{ci} electricity demand commits to 100\% 24/7 carbon-free electricity in 2025, it would reduce Irish emissions by 0.6~Mt\co per year compared to the scenario with no voluntary procurement.
This reduction is equivalent to 14\% of Irish power sector emissions.
100\% annual renewable matching policy can also deliver system-level \co emissions reductions (left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, beyond 85\% CFE target, 24/7 hourly matching achieves greater emissions reductions than 100\% annual mathing.

@@

German consumers have lower average emissions rates due to a cleaner grid than Polish consumers, as one would expect.
In the reference case of grid electricity procurement, the values are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.%
\footnote{For reference, 2021 data for emission intensity of electricity generation was at 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}
Similar to the Irish results, \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} show that in both cases, \gls{ci} participants achieve lower emissions rates with 24/7 hourly CFE procurement than with 100\% annual matching with renewable energy once their CFE targets are tight enough.

>>>>

Voluntary procurement of clean electricity also helps decarbonise electricity system as a whole.
We explore this effect by plotting \co emissions in the local region of the participating consumers, i.e. Ireland.
Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2~Mt\co -- see a reference case in \cref{fig:10-2025-IE-p1-zone_emissions}.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021. A strong decreasing trend is expected, since Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
The modelling results show that if only 10\% of \gls{ci} electricity demand commits to 100\% 24/7 carbon-free electricity in 2025, it would reduce Irish emissions by 0.6~Mt\co per year compared to the scenario with no voluntary procurement.
This reduction is equivalent to 14\% of Irish power sector emissions.
100\% annual renewable matching policy can also deliver system-level \co emissions reductions (left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, beyond 85\% CFE target, 24/7 hourly matching achieves greater emissions reductions than 100\% annual mathing.

@@

German consumers have lower average emissions rates due to a cleaner grid than Polish consumers, as one would expect.
In the reference case of grid electricity procurement, the values are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.%
\footnote{For reference, 2021 data for emission intensity of electricity generation was at 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-GNGEmissionsEU}.}
Similar to the Irish results, \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} show that in both cases, \gls{ci} participants achieve lower emissions rates with 24/7 hourly CFE procurement than with 100\% annual matching with renewable energy once their CFE targets are tight enough.
